% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

\sectionTitle{Professional Experience}{\faSuitcase}
  \begin{experiences}
    \experience
      {Current}
      {Senior Software Developer (Contractor)}{Sky}{London - UK}
      {March 2020}
      {
        \emph{Telecommunication provisioning platform}
        \begin{itemize}
          \item Deployed new microservices bridging Sky with 3rd party api provider
          \item Collaborated remotely with members of team to achieve targets in time without compromising quality
          \item Improved project deployment process
        \end{itemize}
      }
      {Java 11, ActiveMQ, Docker}
      {Kubernetes}
    \emptySeparator
    \experience
      {February 2020}
      {Senior Software Developer (Contractor)}{Loveholidays}{London - UK}
      {March 2019}
      {
        \emph{Holiday planning site and backoffice support system}
        \begin{itemize}
          \item Built microservice from scratch for email integration with backoffice in an effort to centralise communications and automatically process replies and sort them to their corresponding bookings
          \item Improved performance of backoffice by cleaning up the legacy code that was already there and refactoring it when possible to follow better paractices
          \item Refactored backoffice to remove dead code, rearrange module content and organise front end code to make life easier for future developers
          \item Promoted TDD practises and good practices
          \item Support in real time
        \end{itemize}
      }
      {Java 11, Spring Boot, Spring MVC}
      {RabbitMQ, MySQL, JavaScript, Velocity, Kubernetes}
    \emptySeparator
    \experience
      {February 2019}
      {Senior Consultant}{ThoughtWorks}{London - UK}
      {June 2018}
      {
        \emph{Blockchain-based oil trading platform}
        \begin{itemize}
          \item Co-owned front end codebase.
          \item Enhanced incoming request validations with Spring Boot annotations.
          \item Maintained code quality (refactoring, code reviews).
          \item Analysed stories alongside business people.
          \item Set up debugging tools for easier development.
        \end{itemize}
      }
      {React, Redux, Java 8 Streams, NodeJS, Spring Boot}
      {PostgreSQL, AWS, Solidity, Docker, Bash}
    \emptySeparator
    \experience
      {May 2018}
      {Senior Consultant}{ThoughtWorks}{London - UK}
      {March 2017}
      {
        \emph{Event Organisation Digital Platform}
        \begin{itemize}
          \item Collaborated with team to provide a query language for the users of the platform.
          \item Worked with team to split out the authentication into its own service.
          \item Assisted with interviewing for permanent personnel.
        \end{itemize}

        \emph{Navigation application for event spaces}
        \begin{itemize}
          \item Assisted fine tuning the prototype from a previous hackathon.
          \item Arranged the build pipeline on Bamboo CI/CD Server.
          \item Showcased and promoted the application in an event.
        \end{itemize}

        \emph{Integration of event organisation platform with client's main system}
        \begin{itemize}
          \item Co-lead the project.
          \item Supervised the communication with main system development team to coordinate our efforts.
          \item Investigated AWS Lambdas, AWS Queues to specify implementation details.
        \end{itemize}
      }
      {NodeJS, GraphQL, C\#, React, Bamboo CI/CD Server}
      {Redux, OAuth 2.0, .NET Core, EF Core, .NET, Nancy, Android, Google Play Developer Console, Promises, Async/Await, AWS Lambda, AWS SQS, Apigee}
    \emptySeparator

    \experience
      {February 2017}
      {Junior Developer}{Leo Tech Consulting}{London - UK}
      {March 2016}
      {
        \emph{Bet Exchange Platform}
        \begin{itemize}
          \item Refactored existing code for core functionality to a simple workflow using a modified Chain of Responsibility Pattern that made it easier to debug and understand.
          \item Added export capabilities so that the user could get the data and use it as he deemed appropriate.
          \item Demoed product to clients and took part in the planning process.
        \end{itemize}

        \emph{Online Payment Platform}
        \begin{itemize}
          \item Collaborated with a remote team in Singapore to integrate with local online payment service.
        \end{itemize}
      }
      {Groovy, Spring Boot}
      {AngulaJS2, Gradle, MySQL, Grails2, GORM}
    \emptySeparator

    \experience
      {February 2016}
      {Junior Java Developer}{Virtue Fusion}{London - UK}
      {July 2014}
      {
        \emph{Online bingo platform}
        \begin{itemize}
          \item Prioritized and resolved production issues raised by clients in a timely manner.
          \item Implemented game logic for new game features.
          \item Maintained and updated database according to client requests.
        \end{itemize}
      }
      {}
      {Java 7, PL/SQL, Hibernate, EJB}
    \emptySeparator

    \experience
      {June 2013}
      {Web Developer}{Sleeping Sloth}{Lefkosia - Cyprus}
      {November 2012}
      {
        \emph{Co-creator of website for reserving sports facilities in Cyprus}
        \begin{itemize}
          \item Designed database schema and built database abstraction layer.
          \item Built and implemented API for requests to the back-end.
          \item Implemented login and search functionality.
          \item Implemented multi-lingual accessibility.
          \item Communicated with possible customers and discussed functionalities and specifications.
        \end{itemize}
      }
      {PHP, MySQL, JQuery}
      {HTML, CSS}
  \end{experiences}
